

###Problem.  
* There are two problems with the calculation of PEPU cones. I discovered this, because there were a few plants, especially PEPU_802, with huge repro_inv relative to repro_all_count  
* Looking at various data sources I discovered that the estimated FD (Final Development) parts weights for those cones were much too big, for PEPU_802 more than 10x too big  
* In addition, for PEPU_802 and PEPU_807 the aborted cones were actually collected and marked as "to use" in the flower parts data, but aren't being used
* I've looked at Konrad's scripts and can't immediately see what would be wrong
    
```{r}
plot(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

check_FD <-as.data.frame(PEPU_Investment[3])
check_FD_aborted <- subset(check_FD,FD.what=="cone_aborted")
check_FD_aborted

check_parts <- subset(as.data.frame(PEPU_FlowerPartsData),part=="cone_aborted")
check_parts
```

###Problem.  
* As described below, I don't think using a linear fit to estimate leaf growth is appropriate, especially in the older plants
* The plots below show that for all plants, even old ones, if just the upper (narrower diameter) segments are used, the leaf weight vs. diameter plots on the main line
* However, for the points that are "basal diameter,all leaves on plant" or even (diameter of segment 2, leaf weight above segment 2), the diameter increases with little increase in leaf weight  
* this is of course because there are few leaves on the lower branches of an older plant and overall, much lower increase in whole plant leaf weight vs basal diameter  
* this means that for the plots, segment 1 (which are mostly the labeled dots) fall "above" the main line of points; for some individuals segment 2 does the same  
* This leads to an overestimate in leaf weight increase in older plants
* stem weights always look good


* looking at BOLE, age 7
    * colors represent segments, with red the entire plant, then purple, gray, green  
    * for stems, linear no matter what portion plant included  
    * for leaves, with older plants (ages 5,7,9 for BOLE, older for other species) have continued diameter increase with little increase in leaf area  
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
check <- BOLE_HarvestData

plot(dia~stem_weight,data=subset(check), pch=16,log="xy",col=col.lots(segment)
text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check), pch=16,log="xy",col=col.lots(segment)
text(dia~leaf_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
```

* Plot just have age 7 BOLE individuals
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
plot(dia~stem_weight,data=subset(check,age==7), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==7),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==7), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==7),labels=individual,cex=.5,pos=3,offset=-.7)
```

* At the other extreme, with PELA, effect only seed among age 32 plants, and only among 5 of the 7 reps (colors here represent individuals)
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
check <- PELA_HarvestData

plot(dia~stem_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)
```

* Similarly no asymptoting at all for HATE
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
check <- HATE_HarvestData

plot(dia~stem_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)
```

* COER is similar - as are many other species  
* Dots colored by age, only including 7 & 9 year old plants
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
check <- COER_HarvestData

plot(dia~stem_weight,data=subset(check,age>5), pch=16,log="xy",col=col.spp[as.factor(segment)])
text(dia~stem_weight,data=subset(check,segment==1&age>5),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age>5), pch=16,log="xy",col=col.spp[as.factor(segment)])
text(dia~leaf_weight,data=subset(check,segment==1&age>5),labels=individual,cex=.5,pos=3,offset=-.7)
```

###Problem.
* The first plot below shows that there are individuals where absolute investment in accessory tissues is larger than total reproductive investmen* There are two different sources of reproductive investment, one which comes from the file "accessory" and is the sum of all the different accessory tissues and one which comes from the dataframe "investment". The "investment" variant is what is currently being used, but not sure which one should be being used
* They are quite different from each other
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
abline(0,1)
text(120,350,"all RE to accessory tissues",srt=45)

plot(investment$repro_inv~accessory$total_repro_inv,log="xy",pch=16,col=col.spp[as.factor(investment$species)])
```

###Todo.  
* We have never quite finished the calculation for BAER reproductive investment. Right now investment is over-estimated, because the "cone weight" used includes the weight of the "seed pods" (since they are fused to the cone), but there is also a separate weight of "seed pods" included. So the cone weight for each "brown cone" needs to be reduced by the number of seed pods for that cone. If easiest I can do this manually


###ToDo.  
* The total plant weights for many PHPH are a huge underestimate, because they are only the weights of one of several stems emerging from the ground. RA should be accurate, since it is the ratio of reproduction to (growth + repro) on a single stem. But plots of plant size vs. RA will be very strange. Since I don't have repro from the side branches, this means I need (at least for PHPH) to introduce two "plant weight" columns, one to calculate total plant weight, leaf weight, growth, and a second to calculate RA. Happy to take this one myself.
    
###Question.  
* Daniel, you said that there should be graphs stored somewhere from all my .rmd files - I'm not finding these