---
output: html_document
---
#file names
- leaf_counts is file with calculated leaf counts and leaf lifespan data
- LLSummary is file with means of LL - and other variables - by species and age; LMA data is merged to this file
- subsets of LLSummary are created to omit babies or HATE for various analyses 

# general results

- strong correlation between LMA and LL when all species*site combinations included
- LL variable across species, as expected; same for LMA
- LL does not change as plants age; LMA does not change as plants age
- leaf count along the leader decreases in older plants for many species - which is why LL appears to decrease


#next to do

- check how overall plant leaf numbers changes with age, diameter
    
```{r, echo=FALSE,results='hide', message=FALSE}
# load packages
library(tidyr)
library(dplyr)
#library(lme4)

#load files

LMA <- read.csv("data/LMA_short.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE)
#InvestmentSummary <- remake::make("ReproductionAllocation_all")
#names(InvestmentSummary)[1] <- "tag_ID"


#define functions
se <- function(x) sd(x)/sqrt(length(x))
con95 <- function(x) (sd(x)/sqrt(length(x)))*1.96


# leaf lifespan data
raw_leaf_lifespan <- read.csv("data/leaderGrowthLL.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE) %>%
  filter(dont_use!="dead" & dont_use!="dont_use")

# Create new dataset taking only count measures, bc these are ultimately what we want
leaf_lifespan <- raw_leaf_lifespan %>%
  select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

# where counts did not previously exists, set as 0
for(v in c("lvs_start_count","lvs_end_count","lvs_new_count","new_but_shed_count")) {
  i <- is.na(leaf_lifespan[[v]])
  leaf_lifespan[[v]][i] <- 0
}

# For individuals with "length" measures, translate into count

# get average leaves per length for spp
leaves_per_length_spp <- read.csv("data/leaves_per_length.csv", header=TRUE, as.is=TRUE,stringsAsFactors=FALSE) %>%
  filter(use=="yes") %>%
  mutate(count_per_length = leaf_count/length_mm) %>%
  group_by(species) %>%
  summarise(count_per_length = mean(count_per_length, na.rm=TRUE))

# get spp average for all individuals 
raw_leaf_lifespan$count_per_length <- leaves_per_length_spp$count_per_length[match(raw_leaf_lifespan$species, leaves_per_length_spp$species)]

# if possible use data for that individual, if it exists
i <- !is.na(raw_leaf_lifespan$mm_lvs)
raw_leaf_lifespan$count_per_length[i] <- (raw_leaf_lifespan$mm_lvs/raw_leaf_lifespan$count_lvs_spec)[i]

#TODO: Check outlier for HATE


"lvs_start_length""lvs_end_length" "lvs_new_length", ,"mm_lvs_spec","count_lvs_spec"
# #turning NAs into zeros
# colnames(leaf_lifespan)
# leaf_lifespan$lvs_start_length[is.na(leaf_lifespan$lvs_start_length)] <-0
# leaf_lifespan$lvs_start_count[is.na(leaf_lifespan$lvs_start_count)] <-0
# leaf_lifespan$lvs_end_length[is.na(leaf_lifespan$lvs_end_length)] <-0
# leaf_lifespan$lvs_end_count[is.na(leaf_lifespan$lvs_end_count)] <-0
# leaf_lifespan$lvs_new_length[is.na(leaf_lifespan$lvs_new_length)] <-0
# leaf_lifespan$lvs_new_count[is.na(leaf_lifespan$lvs_new_count)] <-0
# leaf_lifespan$new_but_shed_count[is.na(leaf_lifespan$new_but_shed_count)] <-0
# leaf_lifespan$mm_lvs_spec[is.na(leaf_lifespan$mm_lvs_spec)] <-0
# leaf_lifespan$count_lvs_spec[is.na(leaf_lifespan$count_lvs_spec)] <-0



# specific leaves per length data
leaf_lifespan_specific <- subset(leaf_lifespan,mm_lvs_spec!="0")
leaf_lifespan_specific$count_per_length <- leaf_lifespan_specific$count_lvs_spec/leaf_lifespan_specific$mm
leaf_lifespan_specific$leaf_start_total <- leaf_lifespan_specific$lvs_start_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_start_length)
leaf_lifespan_specific$leaf_end_total <- leaf_lifespan_specific$lvs_end_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_end_length)
leaf_lifespan_specific$leaf_new_total <- leaf_lifespan_specific$lvs_new_count + leaf_lifespan_specific$new_but_shed_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_new_length)
head(leaf_lifespan_specific)

#generic leaves per length data
leaves_per_length$count_per_length <- leaves_per_length$leaf_count/leaves_per_length$length_mm
per_length_spp <- aggregate(count_per_length ~ species, leaves_per_length, FUN=mean)

leaf_lifespan_generic <- subset(leaf_lifespan,mm_lvs_spec=="0")
leaf_lifespan_generic <- merge(leaf_lifespan_generic, per_length_spp, by.x="species", by.y="species")
leaf_lifespan_generic$leaf_start_total <- leaf_lifespan_generic$lvs_start_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_start_length)
leaf_lifespan_generic$leaf_end_total <- leaf_lifespan_generic$lvs_end_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_end_length)
leaf_lifespan_generic$leaf_new_total <- leaf_lifespan_generic$lvs_new_count + leaf_lifespan_generic$new_but_shed_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_new_length)
leaf_lifespan_generic <- subset(leaf_lifespan_generic,leaf_new_total>"0")
head(leaf_lifespan_generic)

#combine two files into 1
leaf_counts <- bind_rows(leaf_lifespan_specific, leaf_lifespan_generic)
head(leaf_counts)

#calculating leaf lifespan
leaf_counts$LL_bd <- (leaf_counts$leaf_start_total)/(((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))+(leaf_counts$leaf_new_total)/2)
leaf_counts$LL_death <- (leaf_counts$leaf_start_total)/((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))
leaf_counts$LL_birth <- (leaf_counts$leaf_start_total)/(leaf_counts$leaf_new_total)

leaf_counts$LL_death[which(is.infinite(leaf_counts$LL_death))] <- NA
leaf_counts$LL_bd[which(is.infinite(leaf_counts$LL_death))] <- NA
leaf_counts$LL_birth[which(is.infinite(leaf_counts$LL_death))] <- NA

write.csv(leaf_counts, file = "leaf_counts.csv")

#adding leaf, stem weight data from InvestmentSummary to leaf_counts dataframe
leaf_counts <- left_join(leaf_counts, InvestmentSummary, by = "tag_ID")

#adding columns to leaf_counts to look at change across year
leaf_counts$change_shoot_diam <- leaf_counts$d_end - leaf_counts$d_start
leaf_counts$change_basal_diam <- leaf_counts$FinalBasalDiam - leaf_counts$StartBasalDiam
leaf_counts$change_shoot_area <- (3.14*((leaf_counts$d_end/2)^2)) - (3.14*((leaf_counts$d_start/2)^2))
leaf_counts$change_basal_area <- (3.14*((leaf_counts$FinalBasalDiam/2)^2)) - (3.14*((leaf_counts$StartBasalDiam/2)^2))

#removng crazy numbers
leaf_counts <- subset(leaf_counts,LL_bd>0)
leaf_counts <- subset(leaf_counts,LL_bd<6)
leaf_counts <- subset(leaf_counts,LL_birth<8)
leaf_counts <- subset(leaf_counts,LL_death<8)

#leaf lifespan summary by species, age
LLSummary <- leaf_counts %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length)

#LMA summary by species, age
LMA_summary <- LMA %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), LMA)
names(LMA_summary)<-c("species","age","LMA_mean","LMA_se","LMA_length")

leaf_counts_nobabies <- subset(leaf_counts, age>2)
LMA_nobabies <- subset(LMA, age>2)

#leaf lifespan summary by species
LL_spp <- leaf_counts_nobabies %>%
  group_by(species) %>%
  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth)

#LMA summary by species
LMA_spp <- LMA_nobabies %>%
  group_by(species) %>%
  summarise_each(funs(mean, se, length), LMA)
names(LMA_spp)<-c("species", "LMA_mean","LMA_se","LMA_length")

#merge LMA data into LLSummary dataframe
LLSummary <- merge(LLSummary, LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
LL_spp <- merge(LL_spp, LMA_spp, by.x=c("species"), by.y=c("species"))



#plotting and stats
#LL vs LMA
pch.spp <- c(0,1,2,15,16,17,18,0,1,2,15,16,17,18)
col.spp <- c("red", "dark green", "blue", "purple", "orange", "light green","salmon","turquoise","grey", "black","light blue","brown","yellow","salmon")
col.age <-c("purple","pink","green","orange","blue","light blue")
pch.age <- c(1,1,16,16,16,16)
labels.spp <- c("Banksia","Boronia","Conospermum","Epacris", "Grevillea buxifolia","Grevillea speciosa","Hakea","Hemigenia","Leucopogon","Persoonia", "Petrophile", "Phyllota", "Pimelea", "Pultanaea")
names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU") 
labels.age <- c("1.4","2.4","5","7","9","32")


#remove HATE, babies
LL_nobabies <- subset(LLSummary, age > 2)
LL_noHate <- subset(LLSummary, species != "HATE")
LL_noHatebabies <- subset(LL_nobabies, species != "HATE")
```



# relationship between LMA, LL by age, species

For 2.4 year old plants

```{r, echo=FALSE}
plot(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1)
mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4))
summary(mod)
abline(mod)
```


# Plotting final leaf number on the leader by diameter increase of the entire plant (basal diameter) and the leader (shoot diameter). 

Both show a strong correlation and species effect as expected. For the model with basal diameter there is a strong age effect, but not for shoot diameter. This is presumably because a shoot of a given species should always deploy the same number of leaves for the same diameter increase. In contrast, the whole plant will have many differing shoot numbers with age, so differing effects of a single shoot's increased diameter. Strangely, the model with basal diameter shows a stronger effect between diameter increase and leaf number. 

```{r, echo=FALSE,results='hide', message=FALSE}
plot(change_basal_diam ~ leaf_new_total, leaf_counts, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <- lm(log(leaf_new_total) ~ log(change_basal_diam+1) + species +age, leaf_counts)
summary(mod)

plot(change_shoot_diam ~ leaf_new_total, leaf_counts, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <- lm(log(leaf_new_total) ~ log(change_shoot_diam+10) + species +age, data= subset(leaf_counts, !is.na(change_shoot_diam)))
summary(mod)
```




#LL vs LMA using species by site means

Overall plot shows a lack of relationship when HATE included. This is because it has such a high LMA. The youngest and oldest plants have no pattern, presumably because LL data are inaccurate

```{r, echo=FALSE,results='hide', message=FALSE}

col.LMA <-c("black","purple", "pink", "light green", "orange","blue", "light blue","red")
labels.LMA <-c("all except HATE","age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "including HATE")
plot(LL_birth_mean ~ LMA_mean, LLSummary, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
points(LL_birth_mean ~ LMA_mean, LL_noHate, pch=16, cex=1.2, col=col.age[as.factor(age)])
points(LL_birth_mean ~ LMA_mean, col="red", data=subset(LLSummary, species=="HATE"), pch=17)
mod <- lm(LL_birth_mean ~ LMA_mean, LLSummary)
abline(mod, col="red", lty=2)
mod_no_HATE <- lm(LL_birth_mean ~ LMA_mean, LL_noHate)
abline(mod_no_HATE, lwd=2)
mod_no_HATE5 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==5))
abline(mod_no_HATE5, col="light green", lwd=1.5)
mod_no_HATE7 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==7))
abline(mod_no_HATE7, col="orange", lwd=1.5)
mod_no_HATE9 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==9))
abline(mod_no_HATE9, col="blue", lwd=1.5)
mod_no_HATE2.4 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4))
abline(mod_no_HATE2.4, col="pink", lwd=1.5)
mod_no_HATE1 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age<2.4))
abline(mod_no_HATE1, col="purple", lwd=1.5)
mod_no_HATE32 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==32))
abline(mod_no_HATE32, col="light blue", lwd=1.5)

legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
summary(mod)
```


#Leaf lifespan patterns
First a model showing data by age and species, omitting the youngest plants. Uses calculations for "leaf births" only. Plots of leaf lifespan by age for each of the species

Age is not significant, but some significant interactions (COER, HATE, HEPU)
And many species have sigificantly different LL from one another


```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(LL_birth ~ age +species + age*species, leaf_counts_nobabies)
summary(mod)

leaf_counts %>% group_by(species) %>%
    summarise(mean(age))

plot_LLvAge <- function(spp) {
  plot(LL_birth ~ age, data=subset(leaf_counts,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1, 
     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x")  
}


for(n in names(labels.spp)) {
  plot_LLvAge(n)
}
```




#LMA by age, species, without youngest plants

There is also no overall affect of age on LMA, although a few species would show an effect if analyzed independently. (Again, this model omits 1-year old plants.)

```{r, echo=FALSE, message=FALSE}
plot(LMA_mean ~ as.factor(species), LL_nobabies, xlab="species", ylab="LMA", cex.axis=.8, las=1)
mod <- lm(LMA ~ age +species + age*species, LMA)
summary(mod)

plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="BAER"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Banksia ericifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="BOLE"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Boronia ledifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="COER"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Conospermum ericifolium")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="EPMI"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Epacris microphylla")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="GRBU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Grevillea buxifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="GRSP"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Grevillea speciosa")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="HATE"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Hakea teretifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="HEPU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Hemigenia purpurea")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="LEES"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Leucopogon esquamatus")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PELA"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Persoonia lanceolata")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PEPU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Petrophile pulchella")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PHPH"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Phyllota phylicoides")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PILI"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Pimelea linifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PUTU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Pultenaea tuberculata")
```


#models with leaf counts per age
The number of leaves on a leader is slightly affected by age however, with a decrease in leaf count along the leader with increasing age. This is what gives the perception of fewer leaves in older plants.

QUESTION: Why does age need to be a factor for the plots to work?
```{r, echo=FALSE,results='hide', message=FALSE}
  
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BAER"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Banksia ericifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BOLE"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Boronia ledifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="COER"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Conospermum ericifolium")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="EPMI"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Epacris microphylla")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRBU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Grevillea buxifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRSP"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Grevillea speciosa")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HATE"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Hakea teretifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HEPU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Hemigenia purpurea")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="LEES"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Leucopogon esquamatus")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PELA"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Persoonia lanceolata")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PEPU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Petrophile pulchella")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PHPH"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Phyllota phylicoides")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PILI"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Pimelea linifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PUTU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Pultenaea tuberculata")

mod <- lm(leaf_end_total ~ age +species +age*species, leaf_counts_nobabies)
summary(mod)
```

#models with shoot extenstion by age

###combine shoot extension and investment files, by tag_ID

```{r, echo=FALSE,results='hide', message=FALSE}
plot(new_length_mean ~ age, LLSummary, col=col.spp[as.factor(species)])
legend("topright",col=col.spp, labels.spp, pch=16, cex=1.4)

plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BAER"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Banksia ericifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BOLE"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Boronia ledifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="COER"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Conospermum ericifolium")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="EPMI"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Epacris microphylla")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRBU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Grevillea buxifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRSP"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Grevillea speciosa")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HATE"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Hakea teretifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HEPU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Hemigenia purpurea")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="LEES"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Leucopogon esquamatus")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PELA"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Persoonia lanceolata")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PEPU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Petrophile pulchella")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PHPH"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Phyllota phylicoides")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PILI"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Pimelea linifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PUTU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Pultenaea tuberculata")

mod <- lm(new_length ~ age +species +age*species, leaf_counts)
summary(mod)
```


