nutrient <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")
soil <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nutrient_soil.csv")
accessoryList <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")

library(plyr)
library(dplyr)
library(tidyr)

pch.tissue <- function(x=NULL){
  ret <- c(wood_from_tip=16, wood_from_middle=10,wood_from_base=7,shed_sapwood=1,bark=15,shed_bark=0,leaves=17,senescent_leaves=2,seed=8,reproductive=4)
  names(ret) <- c("wood_from_tip","wood_from_middle","wood_from_base","shed_sapwood","bark","shed_bark","leaves","senescent_leaves","seed","reproductive")
  if(!is.null(x)) {
    ret <- ret[as.character(x)]
  }
  ret
}

pch.tissue2 <- function(x=NULL){
  ret <- c(sapwood=16, bark=15,leaves=17)
  names(ret) <- c("sapwood","bark","leaves")
  if(!is.null(x)) {
    ret <- ret[as.character(x)]
  }
  ret
}

nutrient <- nutrient %>%
  mutate(
    NP = N/P
  )
  


#soils data
```{r}
pdf("figs2/Nutrients/soil.pdf", height=6, width=6)
plot
plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
dev.off()
```



```{r}
nutrient_spp_age <- subset(nutrient,live_dead=="live"|live_dead=="dead")
mean_values <- function(nutrient_spp_age) {
  select(nutrient_spp_age,species,tissue,age,live_dead,K,P,N) %>%
  group_by(species,tissue,age,live_dead) %>%
  summarise_each(funs(mean),N,P,K)
}

nutrient_sum <- mean_values(nutrient_spp_age)

nutrient_sum_N <- select(nutrient_sum,species,tissue,age,live_dead,N)
nutrient_sum_N <- tidyr::spread(nutrient_sum_N,live_dead,N)
names(nutrient_sum_N) <- c("species","tissue","age","N_dead","N_live")

nutrient_sum_P <- select(nutrient_sum,species,tissue,age,live_dead,P)
nutrient_sum_P <- tidyr::spread(nutrient_sum_P,live_dead,P)
names(nutrient_sum_P) <- c("species","tissue","age","P_dead","P_live")

nutrient_sum_K <- select(nutrient_sum,species,tissue,age,live_dead,K)
nutrient_sum_K <- tidyr::spread(nutrient_sum_K,live_dead,K)
names(nutrient_sum_K) <- c("species","tissue","age","K_dead","K_live")

nutrient_sum_spp_age <- plyr::join(nutrient_sum_N, nutrient_sum_P, by = c("species","tissue","age"),type="full")
nutrient_sum_spp_age <- plyr::join(nutrient_sum_spp_age, nutrient_sum_K, by = c("species","tissue","age"),type="full")


nutrient_sum_spp_age <- nutrient_sum_spp_age %>%
  mutate(
    NUE = 1 - (N_dead/N_live),
    PUE = 1 - (P_dead/P_live),
    KUE = 1 - (K_dead/K_live)
  )
```


```{r}
nutrient_spp <- subset(nutrient,live_dead=="live"|live_dead=="dead")
mean_values <- function(nutrient_spp) {
  select(nutrient_spp_age,species,tissue,live_dead,K,P,N) %>%
  group_by(species,tissue,live_dead) %>%
  summarise_each(funs(mean),N,P,K)
}

nutrient_sum <- mean_values(nutrient_spp)

nutrient_sum_N <- select(nutrient_sum,species,tissue,live_dead,N)
nutrient_sum_N <- tidyr::spread(nutrient_sum_N,live_dead,N)
names(nutrient_sum_N) <- c("species","tissue","N_dead","N_live")

nutrient_sum_P <- select(nutrient_sum,species,tissue,live_dead,P)
nutrient_sum_P <- tidyr::spread(nutrient_sum_P,live_dead,P)
names(nutrient_sum_P) <- c("species","tissue","P_dead","P_live")

nutrient_sum_K <- select(nutrient_sum,species,tissue,live_dead,K)
nutrient_sum_K <- tidyr::spread(nutrient_sum_K,live_dead,K)
names(nutrient_sum_K) <- c("species","tissue","K_dead","K_live")

nutrient_sum_spp <- plyr::join(nutrient_sum_N, nutrient_sum_P, by = c("species","tissue"),type="full")
nutrient_sum_spp <- plyr::join(nutrient_sum_spp, nutrient_sum_K, by = c("species","tissue"),type="full")


nutrient_sum_spp <- nutrient_sum_spp %>%
  mutate(
    NUE = 1 - (N_dead/N_live),
    PUE = 1 - (P_dead/P_live),
    KUE = 1 - (K_dead/K_live)
  )
```

convert RA to nutrient values
```{r}
temp <- subset(nutrient_sum_spp,tissue=="leaves")
temp <- select(temp,species,N_dead,N_live,P_dead,P_live)
names(temp) <- c("species","N_dead_leaf","N_live_leaf","P_dead_leaf","P_live_leaf")

SummaryInd2 <- plyr::join(SummaryInd,temp, by="species")
SummaryInd2 <- SummaryInd2 %>% mutate(
  leaf_N_lost = leaf_shed*N_dead_leaf,
  leaf_P_lost = leaf_shed*P_dead_leaf,
  leaf_N_new = leaf_inv_gross*N_live_leaf,
  leaf_P_new = leaf_inv_gross*P_live_leaf,
  leaf_N_net = leaf_N_new - leaf_N_lost,
  leaf_P_net = leaf_P_new - leaf_P_lost
  )
```

Merging in reproduction data
``` {r}
InvestIndPart <- merge(InvestmentByPart,select(accessoryList,-sort), by=c("species","part"))
  
for(v in c("weight")) {
  i <- is.na(InvestIndPart[[v]])
  InvestIndPart[[v]][i] <- 0
}

SummaryInvest <- 
  InvestIndPart %>%
  group_by(parts_fewer_yet,individual) %>%
  summarise_each(funs(sum),weight)

SummaryInvest$species <- SummaryInvest$individual
SummaryInvest$species <- substr(SummaryInvest$species,1,nchar(SummaryInvest$species)-4)
names(SummaryInvest) <- c("tissue","individual","weight","species")

nutrient_subset <- select(nutrient_spp,species,tissue,N,P)

SummaryInvest <- merge(SummaryInvest,nutrient_subset, by=c("species","tissue"),all.x=TRUE)
names(SummaryInvest)

SummaryInvest$tissue_N <- SummaryInvest$weight*SummaryInvest$N
SummaryInvest$tissue_P <- SummaryInvest$weight*SummaryInvest$P

nutrientRepro <- 
  SummaryInvest %>%
  group_by(individual) %>%
  summarise_each(funs(sum),tissue_N,tissue_P)

SummaryInd2 <- plyr::join(SummaryInd2,nutrientRepro, by="individual")

SummaryInd2$RA_N <- SummaryInd2$tissue_N / (SummaryInd2$tissue_N + SummaryInd2$leaf_N_net)
SummaryInd2$RA_P <- SummaryInd2$tissue_P / (SummaryInd2$tissue_P + SummaryInd2$leaf_P_net)

  i <- which(is.infinite(SummaryInd2$RA_N))
  for(v in c("RA_N")) {
    SummaryInd2[[v]][i] <- NA
  }

```

xvar <- "age"
yvar3 <- "RA_N"
yvar2 <- "RA_P"
yvar <- "RA_leaf_area"

data <- subset(SummaryInd2,species!="PEPU")
data <- split(data, data$species)

par(mfrow=c(3,1), cex=1, omi=c(.8,.1,.6,.05), mai=c(.1,.8,.05,.05))

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",ylab=yvar,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",ylab=yvar2,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="x",xlab=xvar,ylab=yvar3,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
  mtext(labels.spp.full(spp),3, outer=TRUE,font=3)
  mtext("age (years)",outer=TRUE,1,line=1.5)
}

  if(spp=="BOLE"|spp=="COER"|spp=="GRSP"|spp=="HEPU") {
    rect(14,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }





plot(RA_N~age,subset(SummaryInd2,species=="BAER"),col=col.age(age),pch=16)  

plot(leaf_N_lost ~ leaf_N_new,SummaryInd2,pch=16,col=col.spp(species),log="xy")
plot(leaf_N_lost ~ leaf_N_new,SummaryInd2,pch=16,col=col.age(age),log="xy")

abline(0,1)
plot(leaf_P_net ~ leaf_N_net,SummaryInd2,pch=16,col=col.spp(species),log="xy")


View(SummaryInd2)
#simple N vs P plot
```{r}
pdf("figs2/Nutrients/NvsP.pdf", height=11, width=8.5)
plot
par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05))
plot(P~N,data=subset(nutrient),col=col.spp(species),pch=pch.tissue(tissue_simple),log="xy")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(P~N,data=subset(nutrient,tissue_simple=="reproductive"|tissue_simple=="seed"),col=col.spp(species),pch=16,log="xy",cex=0.75)
test <- subset(nutrient,tissue_simple=="reproductive"|tissue_simple=="seed")
text(test$P~test$N,labels=test$tissue_complete,cex=0.5,adj=-.2)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()
```

#plotting live versus dead tissue
```{r}
pdf("figs2/Nutrients/live_vs_shed.pdf", height=11, width=8.5)
plot
par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05)) 
plot(P~N,data=subset(nutrient,tissue_complete=="leaves"),col=col.spp(species),pch=16,ylim=c(10,500),log="",xlim=c(.4,2.5))
points(P~N,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1)
text(1.05*par("usr")[1],0.95*par("usr")[4],"leaves versus shed leaves",adj=0)

plot(P~N,data=subset(nutrient,tissue_complete=="bark"),col=col.spp(species),pch=16,ylim=c(10,300),log="",xlim=c(.15,1.5))
points(P~N,data=subset(nutrient,tissue_complete=="shed_bark"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="shed_bark"),col=col.spp(species),pch=1,cex=1)
text(1.05*par("usr")[1],0.95*par("usr")[4],"bark versus shed bark",adj=0)

plot(P~N,data=subset(nutrient,tissue_complete=="wood_from_tip"),col=col.spp(species),pch=16,ylim=c(1,300),log="",xlim=c(0,0.8),cex=1)
points(P~N,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1)
text(1.15*par("usr")[1],0.95*par("usr")[4],"sapwood versus shed sapwood",adj=0)

plot(P~N,data=subset(nutrient,tissue_complete=="wood_from_tip"),col=col.spp(species),pch=16,ylim=c(1,300),log="",xlim=c(0,0.8),cex=1)
points(P~N,data=subset(nutrient,tissue_complete=="wood_from_base"&age>3),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="wood_from_base"&age>3),col=col.spp(species),pch=1,cex=1)
text(1.05*par("usr")[1],0.95*par("usr")[4],"sapwood versus wood from base of plant for plants >3 years",adj=0)

plot(PUE~NUE,data=subset(nutrient_sum_spp_age),col=col.spp(species),pch=pch.tissue2(tissue),log="",xlim=c(-0.5,1),ylim=c(-0.5,1),xlab="NUE vs PUE by species*age")
rect(par("usr")[1],par("usr")[3],0,1.5,col="light gray",border=NA)
rect(par("usr")[1],par("usr")[3],1.5,0,col="light blue",border=NA)
rect(par("usr")[1],par("usr")[3],0,0,col="grey",border=NA)
points(PUE~NUE,data=subset(nutrient_sum_spp_age),col=col.spp(species),pch=pch.tissue2(tissue))
abline(0,1)
legend("topleft",legend=c("sapwood","bark","leaves"),pch=c(16,15,17),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(PUE~NUE,data=subset(nutrient_sum_spp),col=col.spp(species),pch=pch.tissue2(tissue),log="",xlim=c(-0.5,1),ylim=c(-0.5,1),xlab="NUE vs PUE by species")
rect(par("usr")[1],par("usr")[3],0,1.5,col="light gray",border=NA)
rect(par("usr")[1],par("usr")[3],1.5,0,col="light blue",border=NA)
rect(par("usr")[1],par("usr")[3],0,0,col="grey",border=NA)
points(PUE~NUE,data=subset(nutrient_sum_spp),col=col.spp(species),pch=pch.tissue2(tissue))
abline(0,1)
legend("topleft",legend=c("sapwood","bark","leaves"),pch=c(16,15,17),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

dev.off()
```

```{r}
pdf("figs2/Nutrients/age_by_species_NP.pdf", height=7.5, width=11)
plot
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05)) 
for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
data <- subset(nutrient,species==i)
plot(P~N,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(1,200,i)
data2 <- subset(data,tissue_simple=="reproductive"|tissue_simple=="seed")
text(P~N,data2,label=data2$tissue_complete,col="red",cex=0.7)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
}
dev.off()
```



#shed leaf N per year
